Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-04 doc/JFLA2022/paper.tex
add a TODO (alectryon section)

Computability is a key topic in Computer Science teaching. Moreover O'Connor's library is a nice illustration of dependently typed programming, so we chose to devote a full chapter to this formalization, with comments on the definitions and proofs, [counter]-examples and exercises.

We have extracted part of the Goedel library into a new sub-library of the Hydra-battles library: Ackermann.

@@

The hydra-battles book is written in LaTeX, but it makes very frequent references (about once per page, 274 snippets over 281 pages) to parts of the Coq development, showing definitions (Fig.~\ref{fig:Hprime}), lemmas (Fig.~\ref{fig:Ex42E0}), proof scripts (Fig.~\ref{fig:Ex42-schutte}), and computation results (Fig.~\ref{fig:Pow-evalPow17LetIn}).

@@

The transition happened gradually, over a few months: for each snippet of Coq code that was in the book, we had to take the following steps:

>>>>

Computability is a key topic in Computer Science teaching. Moreover O'Connor's library is a nice illustration of dependently typed programming, so we chose to devote a full chapter to this formalization, with comments on the definitions and proofs, [counter]-examples and exercises, and  extract part of the Goedel library into a new sub-library of the Hydra-battles library: Ackermann.

@@

The hydra-battles book is written in LaTeX, but it makes very frequent references (about once per page, 274 snippets over 281 pages) to parts of the Coq development, showing definitions (Fig.~\ref{fig:Hprime}), lemmas (Fig.~\ref{fig:Ex42E0}), proof scripts (Fig.~\ref{fig:Ex42-schutte}), and computation results (Fig.~\ref{fig:Pow-evalPow17LetIn}). The order in which these references appear in the book is independent of the structure of our libraries. Thus, we chose not to include our textbook as comments in the libraries (solution \emph{à la} Coqdoc).
\TODO[Pierre]{is the preceding sentence OK?}

@@

The transition happened gradually, over a few weeks: for each snippet of Coq code that was in the book, we had to take the following steps:
